Type Error Telemetry at Scale

### 2023-09-28 programming23/paper.tex
abstract cleanup

  \paragraph{Context}
  %% What is the broad context of the work? What is
  %% the importance of the general research area?
  {Roblox Studio} lets millions of creators
  build interactive experiences by programming in a variant
  of Lua called Luau.
  The creators form a broad group, ranging from novices writing
  their first script to professional developers, thus Luau
  must support a wide audience.
  As part of its efforts to support all kinds programmers, Luau includes an
  optional, gradual type system and goes to great lengths to minimize false
  positive errors.

  \paragraph{Inquiry}
  %% What problem or question does the paper
  %% address? How has this problem or question been
  %% addressed by others (if at all)?
  Since Luau is currently being used by many creators, we want to collect their feedback
  to improve the language and, in particular, the type system.
  The standard way to collect feedback at a large scale from creators working on
  real projects is to deploy client-side telemetry; however, we cannot
  scrape personal data or proprietary information, which means we cannot
  collect source code fragments, error messages, or even filepaths.
  The research questions are thus how to design a safe telemetry system
  and whether it can provide useful insights about type errors.

>>>>

  \paragraph{Context}
  %% What is the broad context of the work? What is
  %% the importance of the general research area?
  {Roblox Studio} lets millions of creators
  build interactive experiences by programming in a variant
  of Lua called Luau.
  The creators form a broad group, ranging from novices writing
  their first script to professional developers; thus, Luau
  must support a wide audience.
  As part of its efforts to support all kinds programmers, Luau includes an
  optional, gradual type system and goes to great lengths to minimize false
  positive errors.

  \paragraph{Inquiry}
  %% What problem or question does the paper
  %% address? How has this problem or question been
  %% addressed by others (if at all)?
  Since Luau is currently being used by many creators, we want to collect their feedback
  to improve the language and, in particular, the type system.
  The standard way to collect feedback at a large scale from creators working on
  real projects is to deploy client-side telemetry; however, we cannot
  scrape personal data or proprietary information, which means we cannot
  collect source code fragments, error messages, or even filepaths.
  The research questions are thus about how to conduct telemetry that
  is not invasive and obtain insights from it about type errors.
